---
title: "stringsAsFactors = HELLNO"
author: "Jason Sun"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{stringsAsFactors = HELLNO}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

I have developed some new functions based on the previous Jenny Brian's previous fooffactor package and wanna check out the new functionality?

Jason's self made function via `sort_factor()`:

``` r
library(foofactors)
c <- factor(c("character", "hits", "your", "eyeballs")) 
levels(c)
levels(sort_factor(c))
```

Jason's self made function via `check_factor()`:
``` r
library(foofactors)
a <- check_factor(c("character", "hits", "your", "eyeballs")) # This is not a factor
b <- check_factor(c("but", "integer", "where it", "counts", "but")) # This is a factor
```

Can we soften some of their sharp edges?

Binding two factors via `fbind()`:

```{r}
library(foofactors)
a <- factor(c("character", "hits", "your", "eyeballs"))
b <- factor(c("but", "integer", "where it", "counts"))
```

Simply catenating two factors leads to a result that most don't expect.

```{r}
c(a, b)
```

The `fbind()` function glues two factors together and returns factor.

```{r}
fbind(a, b)
```

Often we want a table of frequencies for the levels of a factor. The base `table()` function returns an object of class `table`, which can be inconvenient for downstream work.  Processing with `as.data.frame()` can be helpful but it's a bit clunky.

```{r}
set.seed(1234)
x <- factor(sample(letters[1:5], size = 100, replace = TRUE))
table(x)
as.data.frame(table(x))
```

The `freq_out()` function returns a frequency table as a well-named `tbl_df`:

```{r}
freq_out(x)
```

